\vspace{-1cm}\Large{\textsf{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China} \\ \textsf{Replication Instructions}}

### 2020-01-21 Documentation/Replication_Instruction.tex
data_rev_v2

This note explains step-by-step how to replicate all the results in \textit{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China}. We begin with some housekeeping stuff in Section \rom{1}. Section \rom{2} explains in detail how to replicate all the results in the main text. Section \rom{3} shows how the results in the appendices can be replicated. The data and code can be downloaded from the AEA Data and Code Repository (OPENICPSR-112005).

@@

The readers will get a number of files for replicating the results. To ease digestion, we briefly introduce the structure of the folders and files. As typographical convention, we use \bcode{blue computer modern typewriter} to indicate \bcode{folders} and \bcode{files}. The parent folder is referred to as \bcode{./}.
\begin{itemize}
    \item
    \bcode{./Empirical/}:
    \begin{itemize}
        \item
        \bcode{./Data/}: contains the raw and cleaned data.
        \item
        \bcode{./Results/}: contains all the figures and log-files.
        \item
        \bcode{./cpsc\_raw.do}: does initial processing of the NGSPS.
        \item
        \bcode{./cec\_clean.do}: does initial processing of the CNEC.
        \item
        \bcode{./cpsc\_convert.R}: converts the NGSPS to the binary format of \code{R}.
        \item
        \bcode{./cec\_convert.R}: converts the CNEC to the binary format of \code{R}.
        \item
        \bcode{./Empirical\_AEJ.R}: produces most empirical results in the main text.
        \item
        \bcode{./Empirical\_Appendix.R} produces most empirical results in the appendices.
        \item
        \bcode{./Accounting.R}: executes the accounting exercise.
        \item
        \bcode{./Descriptive.R}: computes some summary statistics of the NGSPS.
    \end{itemize}
    \item
    \bcode{./Quantitative/}
    \begin{itemize}
        \item
        \bcode{./Results/}: contains all the results and figures.
        \item
        \bcode{./twosectors.m}: computes the equilibrium of the two-sector model with perfect substitution used in the main text and saves the results in \bcode{.mat} format.
        \item
        \bcode{./fcn2.m}: computes the excess demand at a given vector of price; called by \bcode{twosectors.m}.
        \item
        \bcode{./generate\_tables\_main.m}: prints Tables 4, 5 and 6 in the main text.
        \item
        \bcode{./plot\_figures.m}: plots Figures 5 and 6 in the main text.
        \item
        \bcode{./twosectors\_ces.m}: computes the equilibrium of the two-sector model with constant elasticity of substitution used in Appendix J and saves the results in \bcode{.mat} format.
        \item
        \bcode{./fcnces.m}: computes the excess demand at a given vector of price; called by \\
        \bcode{twosectors\_ces.m}.
        \item
        \bcode{./generate\_tables\_appendix.m}: prints Table J.1 in Appendix J.
        \item
        \bcode{./misc.m}: draws Figure D.2 and computes the decomposition in Sections \rom{4}.A and \rom{4}.B of the main text.
    \end{itemize}
\end{itemize}

@@

In what follows, we will only use the files converted by \code{R}. A list of the essential files is provided below. All the files should be placed under \bcode{./Empirical/Data/}. For ease of reference, we use the two-letter acronyms in parenthesis when referring to the data files later.
\begin{itemize}
    \item
    \bcode{KEYFIRM\_R.RData (PK)}: Key sources of the NGSPS.
    \item
    \bcode{ALLFIRM\_R.RData (PA)}: All sources of the NGSPS.
    \item
    \bcode{CNEC\_avgp.RData (CA)}: All samples in the CNEC.
    \item
    \bcode{DLARGE\_R.RData (DL)}: A subset of \code{CA} which overlaps with the 2004 ASIF.
    \item
    \bcode{susb04.csv (US)}: SUSB 2004.
\end{itemize}
Because we cannot post the NGSPS and CNEC publicly, the readers will not be able to run some of the files. Tables \ref{tab:navi_main} and \ref{tab:navi_appendix} list respectively which part of each file depends on which datasets and generates which result; the datasets are referenced using the above two-letter acronyms.

>>>>

This note explains step-by-step how to replicate all the results in \textit{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China}. We begin with some housekeeping information in Section \rom{1}. Section \rom{2} explains in detail how to replicate all the results in the main text. Section \rom{3} shows how the results in the appendices can be replicated. The data and code can be downloaded from the AEA Data and Code Repository (OPENICPSR-112005).

@@

The readers will get a number of files for replicating the results. To facilitate digestion, we briefly introduce the structure of the folders and files. As typographical convention, we use \bcode{blue computer modern typewriter} to indicate \bcode{folders} and \bcode{files}. The parent folder is referred to as \bcode{./}.
\begin{itemize}
    \item
    \bcode{./Empirical/}:
    \begin{itemize}
        \item
        \bcode{./Data/}: contains the raw and cleaned data.
        \item
        \bcode{./Results/}: contains all the figures and log-files.
        \item
        \bcode{./cpsc\_raw.do}: does initial processing of the NGSPS.
        \item
        \bcode{./cec\_clean.do}: does initial processing of the CNEC.
        \item
        \bcode{./cpsc\_convert.R}: converts the NGSPS to the binary format of \code{R}.
        \item
        \bcode{./cec\_convert.R}: converts the CNEC to the binary format of \code{R}.
        \item
        \bcode{./Empirical\_AEJ.R}: produces most empirical results in the main text.
        \item
        \bcode{./Empirical\_Appendix.R} produces most empirical results in the appendices.
        \item
        \bcode{./Empirical\_Public\_Data.R} produces the empirical results reproducible using the published data (SUSB): the U.S. firm size distributions in Figures 2 and E.1 (blue bars).
        \item
        \bcode{./Accounting.R}: executes the accounting exercise.
        \item
        \bcode{./Descriptive.R}: computes some summary statistics of the NGSPS.
    \end{itemize}
    \item
    \bcode{./Quantitative/}
    \begin{itemize}
        \item
        \bcode{./Results/}: contains all the results and figures.
        \item
        \bcode{./twosectors.m}: computes the equilibrium of the two-sector model with perfect substitution used in the main text and saves the results in \bcode{.mat} format.
        \item
        \bcode{./fcn2.m}: computes the excess demand at a given vector of price; called by \bcode{twosectors.m}.
        \item
        \bcode{./generate\_tables\_main.m}: prints Tables 4, 5 and 6 in the main text.
        \item
        \bcode{./plot\_figures.m}: plots Figures 5 and 6 in the main text.
        \item
        \bcode{./twosectors\_ces.m}: computes the equilibrium of the two-sector model with constant elasticity of substitution used in Appendix J and saves the results in \bcode{.mat} format.
        \item
        \bcode{./fcnces.m}: computes the excess demand at a given vector of price; called by \\
        \bcode{twosectors\_ces.m}.
        \item
        \bcode{./generate\_tables\_appendix.m}: prints Table J.1 in Appendix J.
        \item
        \bcode{./misc.m}: draws Figure D.2 and computes the decomposition in Sections \rom{4}.A and \rom{4}.B of the main text.
    \end{itemize}
\end{itemize}

@@

\subsection{Reproducibility Using the Published Data}

In what follows, we will only use the files converted by \code{R}. A list of the essential files is provided below. All the files should be placed under \bcode{./Empirical/Data/}. For ease of reference, we use the two-letter acronyms in parenthesis when referring to the data files later.
\begin{itemize}
    \item
    \bcode{KEYFIRM\_R.RData (PK)}: Key sources of the NGSPS.
    \item
    \bcode{ALLFIRM\_R.RData (PA)}: All sources of the NGSPS.
    \item
    \bcode{CNEC\_avgp.RData (CA)}: All samples in the CNEC.
    \item
    \bcode{DLARGE\_R.RData (DL)}: A subset of \code{CA} which overlaps with the 2004 ASIF.
    \item
    \bcode{susb04.csv (US)}: SUSB 2004.
\end{itemize}
Because we cannot post the NGSPS and CNEC publicly, the readers will not be able to run some of the files. Tables \ref{tab:navi_main} and \ref{tab:navi_appendix} list respectively which part of each file depends on which datasets and generates which result; the datasets are referenced using the above two-letter acronyms. With the published data, for the empirical part, the readers would be able to replicate the U.S. firm size distributions in Figure 2 and E.1 (the blue bars); program \bcode{Empirical\-Public\_Data.R} does the job. The program is constructed by taking the relevant code snippet from \bcode{Empirical\_AEJ.R} (Section 3) and \bcode{Empirical\_Appendix.R} (Section 5), as can be seen by direct comparison between the files. All the quantitative results can be replicated using the programs provided.
